---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metaSVR

<!-- badges: start -->
<!-- badges: end -->

metaSVR is an R Package to integrates Support Vector Regression (SVR) with various metaheuristic algorithms for automated hyperparameter tuning which is: Cost, Gamma, and Epsilon.

This package can be used to do prediction using SVR for small dataset and to do task where required optimal performance, such as forecasting renewable energy production, forecasting air pollutant, or modelling any regression that involve nonlinear patterns.    

## Features

Features provided in this package including:
- Hybrid of SVR with some metaheuristic algorithms such as:
  - Archimedes Optimization (AO)
  - Coot Bird Optimization (CBO)
  - Combined Archimedes Optimization with Coot Bird Optimization (AOCBO)
  - Harris Hawks Optimization (HHO)
  - Grey Wolf Optimizer (GWO)
  - Ant Lion Optimization (ALO)
  - Enhanced Harris Hawks Optimization with Coot Bird Optimization (EHHOCBO)
- SVR can be customized by kernel, options: radial, polynomial, sigmoid.
- Multiple objective function can be used, options: sMAPE, MAPE, RMSE, MAE
- Flexible hyperparameter search space for cost, gamma, and epsilon
- Built-in data with min-max normalization and automatic denormalization handling of prediction result.
- Output produced best parameter set, iteration history, time used, and evaluation metrics. 

## Installation

You can install the development version of metaSVR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rechtianaputri/metaSVR")
```

## Example

Here is a simple usage example of metaSVR using synthetic data:

```{r example}
library(metaSVR)

#Generate synthetic data
set.seed(123)
x <- matrix(rnorm(100), ncol = 2)
y <- x[,1] * 3 + rnorm(50)

# Run SVR Hybird with AOCBO
result <- svrHybrid(x_train = x[1:40,], y_train = y[1:40],
                   x_test = x[41:50,], y_test = y[41:50],
                   kernel = "radial", optimizer = "AOCBO",
                   objective = "SMAPE", is.y.normalize = FALSE,
                   max_iter = 100, N = 40)

# Access Results
result$best_params # show the best parameter result
result$total_iter # show total iteration to optimize
result$model # SVR model optimizing by metaheuristic algorithms
result$time # Time used to generate optimization
```

## Documentation

Each metaheuristic is implemented as a standalone optimizer, used by each optimization to improve SVR. For full documentation see the help files:
```{r}
?svrHybrid
?AO
?CBO
?AOCBO
?loss_calculate
```

